How cryptic is cryptic diversity? \newline Machine learning approaches to fine scale variation in the morphology of \textit{Emys marmorata}.

### 2013-06-19 documents/turtle_presentation.Rnw
final draft?

\begin{frame}
  \frametitle{Generalize using best random forest model}
<<>>=
oo <- Reduce(cbind, Map(function(x) x$t, rr))
colnames(oo) <- groups
dd <- melt(oo)
gdist <- ggplot(dd, aes(x = value, fill = X2)) + geom_density(alpha = 0.5,
                                                              size = 0.1)
gdist <- gdist + theme(legend.position = 'none',
                       #legend.title = element_blank(),
                       #legend.margin = unit(0, 'cm'),
                       #legend.text = element_blank(),
                       axis.title = element_text(size = 8),
                       axis.text = element_text(size = 5))
gdist <- gdist + scale_fill_manual(name = '', values = cbp)

@@

\begin{frame}[fragile]
  \frametitle{Variable importance of random forest model}
  % ggpairs from the best random forest model
<<imp, fig.width = 3.5, fig.height = 3.5, eval = TRUE>>=
most.imp <- trf.a$spinks$optVariables
ww <- 'spinks'
ggimp <- ggpairs(turtle.adult,
                 columns = c(most.imp[1:3], ww), 
                 colour = 'spinks',
                 upper = 'blank',
                 params = c(LabelSize = 2, gridLabelSize = 2, size = 1))

>>>>

\begin{frame}
  \frametitle{Generalize using best random forest model}
<<>>=
oo <- Reduce(cbind, Map(function(x) x$t, rr))
colnames(oo) <- groups
dd <- melt(oo)
gdist <- ggplot(dd, aes(x = value, fill = X2)) + geom_density(alpha = 0.5,
                                                              size = 0.1)
gdist <- gdist + theme(#legend.position = 'none',
                       legend.title = element_blank(),
                       legend.margin = unit(0, 'cm'),
                       #legend.text = element_blank(),
                       axis.title = element_text(size = 8),
                       axis.text = element_text(size = 5))
gdist <- gdist + scale_fill_manual(name = '', values = cbp,
                                   labels = c('morph 1', 'morph 2',
                                              'molec 1', 'molec 2'))

@@

\begin{frame}[fragile]
  \frametitle{Variable importance of random forest model}
  % ggpairs from the best random forest model
<<imp, fig.width = 3.5, fig.height = 3.5, eval = TRUE>>=
most.imp <- trf.a$spinks$optVariables
ww <- 'spinks'
ggimp <- ggpairs(turtle.adult,
                 columns = c(most.imp[1:3], ww), 
                 colour = 'spinks',
                 upper = 'blank',
                 params = c(LabelSize = 2, gridLabelSize = 2, size = 1))
classlab <- ggally_text('molec 2', size = 3)

ggimp <- putPlot(ggimp, classlab, 4, 4)
